---
title: "Classification Example"
output: html_notebook
---

Benchmarking three diverse learners for a classification task








































Set Up the Environment

- Set a seed for reproducibility
- Install packages
- Load libraries

```{r}
### Set seed ###

set.seed(78)

### Packages and Libraries ###

# install.packages("knitr")
# install.packages("mlr3verse")

library(knitr) # for pretty tables
library(mlr3verse)
```


























Load Your Data

`penguins` is a built-in classification task

```{r}
# create task object
task = tsk("penguins")

task

task$missings()
```






























Define learners

- `classif.rpart`
- `classif.naive_bayes`
- `classif.xgboost`

Things to look for:

1. Feature Types
  a. integer
  b. numeric
  c. factor
2. Properties
  a. multiclass
  b. missings

```{r}
lrn("classif.rpart")

lrn("classif.naive_bayes") # missing missings

lrn("classif.xgboost") # missing factor
```


















Define pipeOps

`classif.rpart` requires no preprocessing
`classif.naive_bayes` requires imputation
`classif.xgboost` requires encoding

```{r}
impute = po("imputesample", id="impute")

encode = po("encode", id="encode")
```































Create Learners

`rpart`
```{r}
rpart = lrn("classif.rpart", id="rpart")
```



`naive_bayes`
```{r}
lrnr = po("learner", lrn("classif.naive_bayes"), id="naive_bayes")

graph = impute %>>% lrnr

graph$plot(html=T)

naive_bayes = as_learner(graph)
```



`xgboost`
```{r}
lrnr = po("learner", lrn("classif.xgboost"), id="xgboost")

graph = encode %>>% lrnr

graph$plot(html=T)

xgboost = as_learner(graph)
```










Resampling

```{r}
# create a resampling object
cv = rsmp("cv", folds=10)
```




































Benchmarking

```{r}
design = benchmark_grid(
  task = task,
  learners = c(rpart, naive_bayes, xgboost),
  resampling = cv
)

bmr = benchmark(design)
```































Results!

```{r}
# define the performance measure
measure = msr("classif.ce")

# aggregate the results over resamplings
table = bmr$aggregate(measure)

kable(table)
```






















































