---
title: "Regression Example"
output: html_notebook
---

Benchmarking diverse learners for a regression task


Set Up the Environment

- Set a seed for reproducibility
- Install packages
- Load libraries

```{r}
### Set seed ###

set.seed(78)

### Packages and Libraries ###

# install.packages("mlr3verse")

library(mlr3verse)
```


Load Your Data

`bike_sharing` is a built-in regression task

```{r}
# create task object
task = tsk("bike_sharing")

task$data()

task$missings()
```


Explore learners

Things to look for:

1. Feature Types
  a. logical
  b. integer
  c. numeric
  d. character
  e. factor


```{r}
featureless = lrn("regr.featureless", id = "featureless") # no preprocessing

ranger = lrn("regr.ranger", id = "ranger") # no preprocessing

lm = lrn("regr.lm") # must preprocess date and categorical features

rpart = lrn("regr.rpart") # must preprocess date and categorical features

svm = lrn("regr.svm") # must preprocess date and categorical features

xgboost = lrn("regr.xgboost") # must preprocess date and categorical features
```


Create pipeOps

```{r}
# create POSIXct type date from character date
dateMutate = po("mutate", id="dateToPOSIXct")
dateMutate$param_set$values$mutation = list(
  date = ~ as.POSIXct(date, format="%Y-%m-%d", tz="UTC")
)

# encode the POSIXct type date into year, month, day columns
dateFeatures = po("datefeatures", param_vals = list(
  cyclic = FALSE, 
  hour = FALSE, 
  minute = FALSE, 
  second = FALSE, 
  is_day = FALSE, 
  keep_date_var = FALSE))

# encode categorical features
encode = po("encode")
```


Create graph learners

```{r}
# rpart
graph1 = dateMutate %>>% dateFeatures %>>% po("learner", rpart)

graph1$plot(html = TRUE)

rpart = as_learner(graph1)

rpart$id = "rpart"



# svm
graph2 = dateMutate %>>% dateFeatures %>>% encode %>>% po("learner", svm)

svm = as_learner(graph2)

svm$id = "svm"



# xgboost
graph3 = dateMutate %>>% dateFeatures %>>% encode %>>% po("learner", xgboost)

xgboost = as_learner(graph3)

xgboost$id = "xgboost"



# lm
graph4 = dateMutate %>>% dateFeatures %>>% encode %>>% po("learner", lm)

lm = as_learner(graph4)

lm$id = "lm"
```


Resampling

```{r}
# create a resampling object
cv = rsmp("cv", folds=10)
```


Benchmarking

```{r}
design = benchmark_grid(
  task = task,
  learners = c(ranger, rpart, svm, xgboost, lm, featureless),
  resampling = cv
)

bmr = benchmark(design)
```


Results!

```{r}
# define the performance measure
measure = msr("regr.rmse")

# aggregate the results over resamplings
bmr$aggregate(measure)
```



```{r}
autoplot(bmr)
```




